---
title: "reproduciblePitch"
author: "Yangyang Liu"
date: "2023-09-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coursera Reproducible Pitch

### About the Course Project

This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

### How to use the application

This application to calculate work hours, overtime, and pay with tax and after-tax considerations can be quite involved due to the complexity of payroll calculations.

The application is running on (http://127.0.0.1:6058)

ui.R, and Server.R Code in my github repository (https://github.com/yali0826/Coursera-Data-Product-Assignment--week2/blob/main/Shiny-Application/app.R)


```{r summary}
library(shiny)
```

## Data used in the app

ui.R

r sidebarLayout(
    sidebarPanel(
      numericInput("hours_worked", "Hours Worked:", 40, min = 0),
      numericInput("hourly_rate", "Hourly Rate ($):", 15, min = 0),
      numericInput("overtime_threshold", "Overtime Threshold (hours):", 40, min = 0),
      numericInput("tax_rate", "Tax Rate (%):", 20, min = 0),
      actionButton("calculate_button", "Calculate")
    ),
    mainPanel(
      h4("Payroll Results:"),
      textOutput("gross_pay"),
      textOutput("tax_deduction"),
      textOutput("net_pay")
    )
  )
)


server.R
server <- function(input, output) {
  observeEvent(input$calculate_button, {
    # Calculate gross pay
    hours_worked <- input$hours_worked
    hourly_rate <- input$hourly_rate
    overtime_threshold <- input$overtime_threshold
    tax_rate <- input$tax_rate
    
    if (hours_worked > overtime_threshold) {
      regular_hours <- overtime_threshold
      overtime_hours <- hours_worked - overtime_threshold
    } else {
      regular_hours <- hours_worked
      overtime_hours <- 0
    }
    
    gross_pay <- (regular_hours * hourly_rate) + (overtime_hours * hourly_rate * 1.5)
    
    # Calculate tax deduction
    tax_deduction <- (gross_pay * (tax_rate / 100))
    
    # Calculate net pay
    net_pay <- gross_pay - tax_deduction
    
    # Update the output elements
    output$gross_pay <- renderText({
      paste("Gross Pay: $", formatC(gross_pay, format = "f", digits = 2))
    })
    
    output$tax_deduction <- renderText({
      paste("Tax Deduction: $", formatC(tax_deduction, format = "f", digits = 2))
    })
    
    output$net_pay <- renderText({
      paste("Net Pay: $", formatC(net_pay, format = "f", digits = 2))
    })
  })
}
```

## Both file be found here: 

### Main panel

- Hours Worked
- Hourly Rate
- Overtme Thereshold
- Tax Rate

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
